Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-21 sections/tensors.tex
Update on Overleaf.

To build our bridge, we embrace a set of abstractions: level formats/Fiber Trees, iteration context dependent instantiation of iterators, and tensor life cycles.
%
Our first abstraction mostly already exists in the literature: a manner of specifying a data structure for a multi-dimensional tensor out of data structures for single dimensional tensors~\cite{sze2017efficient ,chou2022compilation, chou2018format}. 
%
We recapitulate the essential details here.
%
Our next two abstractions adds to to the first by providing a mechanism to use data structures generated by the first abstraction in a greater variety of contexts while maintaining per-dimension encapsulation of array data structures.
%
Previous efforts to compiler a greater variety of sparse array programs left these bridges untouched ~\cite{henry_compilation_2021, won2023unified, senanayake2020sparse}.
%
%
% As we will see
% \begin{enumerate}
%     \item Compilation substitutes in different iterators depending on context, mainly the traversal pattern of the iterator (oh god).
%     \item Less obviously, iterators have other state that needs to be tracked, such as when we write stuff.
%     \item how do we ask for the right iterator and how do we change/manage their state?
% \end{enumerate}
% Need to Make these problems clear by this point, hope that read anticipate them.

% Solutions:
% \begin{enumerate}
%     \item Einsum like: limit when state can change, leading to a natural lifecycle for a tensor.
%     \item simple interface to go from an index expression into an iterator that decomposes in a way tensor compilers are used to.
% \end{enumerate}

@@

\begin{enumerate}
\item fibers
\item assembly
\item reassembly
\end{enumerate}

>>>>

To build our bridge, we embrace a set of abstractions: level formats/Fiber Trees, iteration context dependent instantiation of iterators, and tensor life cycles.
%
Our first abstraction mostly already exists in the literature: a manner of specifying a data structure for a multi-dimensional tensor out of data structures for single dimensional tensors~\cite{sze2017efficient,chou2022compilation, chou2018format}. 
%
We recapitulate the essential details here.
%
Our next two abstractions adds to to the first by providing a mechanism to use data structures generated by the first abstraction in a greater variety of contexts while maintaining per-dimension encapsulation of array data structures.
%
Previous efforts to compiler a greater variety of sparse array programs left these bridges untouched ~\cite{henry_compilation_2021, won2023unified, senanayake2020sparse}.
%
We introduce an interface to instatiate iterators in a variety of contexts in our programs and we introduce the lifecycle interface to manage when we read and write to multi-dimensional iterators.
%
These interfaces add to the level abstraction.

@@

\begin{enumerate}
\item fibers and levels
\item assembly
\item reassembly
\end{enumerate}
